---
title: "475 Analysis"
output: html_document
date: "2024-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Setup

#load packages
library(quantmod)
library(expss)
library(vtable)
library(xts)
library(tidyr)
library(tidyverse)
library(dplyr)
library(stringi)
library(estimatr)
library(stargazer)
library(sandwich)
library(ggpubr)


```

```{r}
##################################################
## PART A: SETUP & DATA CLEANING                 #
##################################################

# Load primary dataset
housing.raw <- read.csv("Data/housing_indicators_micro.csv")
cols <- c("Census.year..2.", "GEO", "DGUID", "Housing.indicators..9.",
          "Tenure..4.", "VALUE") # cols to keep
housing <- housing.raw[,cols] 
names(housing) <- c("Year", "GEO", "DGUID", "Indicator", "Tenure", "VALUE")

```

```{r}
housing.w <- pivot_wider(housing, id_cols=c("Year", "GEO", "DGUID","Tenure"),
                         names_from="Indicator", values_from="VALUE")
cols <- c("Year", "GEO", "DGUID", "Tenure", "tot.hh", "inadq.pc", "unsuit.pc",
          "unafford.pc", "core.nd", "core.nd.pc", "inadq", "unsuit", "unafford")
names(housing.w) <- cols

housing.w$Tenure[housing.w$Tenure == "Dwelling provided by the local government, First Nation or Indian band"] <- "Government provided"

housing.w$Tenure[housing.w$Tenure == "Total - Tenure"] <- "Total"

# drop government provided tenure values - not relevant
housing.w <- housing.w %>% filter(Tenure!="Government provided")

# replace NAs with zeros

housing.w <- housing.w %>% replace_na(list(tot.hh=0))
#housing.w <- housing.w %>% replace_na(list(tot.hh=0, inadq.pc=0.0, unsuit.pc=0.0, unafford.pc=0.0,
#                              core.nd=0, core.nd.pc=0.0, inadq=0, unsuit=0, unafford=0))

# drop subdivisions where tot.hh for total tenure == 0
housing.total <- filter(housing.w, Tenure == "Total" )
# filter df by Tenure == Tenure total
for (i in 1:nrow(housing.total)) {
  if (housing.total[i, "tot.hh"] == 0) {
    yr <- as.numeric(housing.total[i, "Year"]) # if tot.hh == 0, collect year and DGUID
    geo_id <- as.character(housing.total[i, "DGUID"])
    
    # in orig df, drop observation if year and DGUID match
    housing.w <- housing.w %>% subset(!(DGUID==geo_id & Year==yr))
  }
}



```



```{r}
census <- read.csv("C:/Users/marti/Documents/_ECO475 Term Paper/Data/census_2021.csv")
```

```{r}
# Filter Census data to geos, variables of interest

# characteristics/controls of interest
chars_of_int <- c(1,2,3,140,1403,1526,6,80,81,244,
                  360,1457,1458,1459,1460,
                  1461,1462,1463,1464,2016,2017,
                  2230,139) 
census.f <- census %>% filter(GEO_LEVEL == "Census subdivision" & CHARACTERISTIC_ID %in% chars_of_int)

# Grab only columns of interest
cols_of_int <- c("DGUID", "GEO_NAME", "CHARACTERISTIC_ID", "CHARACTERISTIC_NAME",
                 "C1_COUNT_TOTAL", "C10_RATE_TOTAL")
census.f <- census.f[,cols_of_int]


# Create value column. If population, use count var. Else, use rate
census.f$VALUE <- NA

for (i in 1:nrow(census.f)) {
if (census.f[i,"CHARACTERISTIC_ID"] %in% c(1,2,3,140)) {
  census.f[i,"VALUE"] <- census.f[i,"C1_COUNT_TOTAL"]
} else {
  census.f[i,"VALUE"] <- census.f[i,"C10_RATE_TOTAL"]
}
}

```

```{r}
# Convert to wide
## Change characteristic names so they are shorter and more manageable
name.chg <- list(c("Population, 2021", "pop21"),
                 c("Population, 2016", "pop16"),
                 c("Population percentage change, 2016 to 2021", "pop_chg"),
                 c("Population density per square kilometre", "pop_dens"),
                 c("    Married couples", "married"),
                 c("      With children", "marr_w_child"),
                 c("  Median after-tax income of household in 2020 ($)", "med_at_inc"),
                 c("Prevalence of low income based on the Low-income cut-offs, after tax (LICO-AT) (%)", "bel_lico"),
                 c("  Indigenous identity", "indig"),
                 c("  15 to 24 years", "age_15to24"),
                 c("  25 to 34 years", "age_25to34"),
                 c("  35 to 44 years", "age_35to44"),
                 c("  45 to 54 years", "age_45to54"),
                 c("  55 to 64 years", "age_55to64"),
                 c("  65 to 74 years", "age_65to74"),
                 c("  75 to 84 years", "age_75to84"),
                 c("  85 years and over", "age_85_plus"),
                 c("  Not Canadian citizens", "non_cdn"),
                 c("  High (secondary) school diploma or equivalency certificate", "he_highschool"),
                 c("  Postsecondary certificate, diploma or degree", "he_postsec"),
                 c("Unemployment rate", "unemp"),
                 c("  Number of COVID-19 emergency and recovery benefits recipients aged 15 years and over in private households in 2020 - 25% sample data", "cov19aid.pc"),
                 c("    Average COVID-19 emergency and recovery benefits in 2020 among recipients ($)","av_cov19aid"))

for (name in name.chg) {
  census.f[census.f$CHARACTERISTIC_NAME == name[1], "CHARACTERISTIC_NAME"] <- name[2]
}

## Create wide dataset
census.w <- census.f %>% pivot_wider(id_cols=c("DGUID", "GEO_NAME"),
                         names_from="CHARACTERISTIC_NAME", values_from="VALUE")

# Merge with housing indicator set
full.df <- left_join(housing.w, census.w, by=join_by(DGUID))

```

```{r}
geo_list <- as.data.frame(unique(full.df$GEO_NAME))
```

```{r}
# EXTRA VARIABLES TO CREATE
## Indigenous reserve - if GEO_NAME contains (IRI)
full.df$indig_res = 0
for (i in 1:nrow(full.df)){
  recoded_str <- as.character(full.df[i,"GEO_NAME"]) %>% iconv(from="utf-8", to="ascii")
  sample_s <- str_sub(recoded_str, -6)
  if (grepl("(IRI)", sample_s)) {
    full.df[i,"indig_res"] <- 1
  }
} # the str_sub fcn does not like french accented characters. Function iconv converted the
  # text to ascii which it did accept without issue. 



## Provinces
### Note: Province codes are a two-character string starting AFTER the first 9 "Fixed width" 
### characters in the DGUID.
provinces <- list(c(10, "NL"),
                  c(11, "PEI"),
                  c(12, "NS"),
                  c(13, "NB"),
                  c(24, "QC"),
                  c(35, "ON"),
                  c(46, "MB"),
                  c(47, "SK"),
                  c(48, "AB"),
                  c(59, "BC"),
                  c(60, "YT"),
                  c(61, "NT"),
                  c(62, "NU"))

full.df$prov <- NA
for (i in 1:nrow(full.df)){
  pr_sub <- as.numeric(substr(full.df[i,"DGUID"], 10, 11))
  for (j in provinces){
    if (pr_sub == j[1]){
      full.df[i,"prov"] <- j[2]
    }
  }
}

## Population Bins

### Going to group as follows based on 2021 pop: 0 to <1000, 1000 to <2500, 
### 2500 to <10000, 10000 to <50000, 50000 to <200000, >=200000

### order: list(var_name, lower_bound, upper_bound)
city_params <- list(
  list("pop_bel_1k", 0, 1000, "Below 1000"),
  list("pop_1k_2.5k", 1000, 2500, "1000 to 2500"),
  list("pop_2.5k_10k", 2500, 10000, "2500 to 10,000"),
  list("pop_10k_50k", 10000, 50000, "10,000 to 50,000"),
  list("pop_50k_200k", 50000, 200000, "50,000 to 200,000"),
  list("pop_abv_200k", 200000, max(full.df$pop21, na.rm=TRUE) + 1, "over 200,000") # max value plus 1, see comment below 
  ### because will use < for second value. see code below.
)

full.df$pop.bin <- "" # Adding a category column for the dummies above to assist group_by's

for (var in city_params){
  col_nam <- as.character(var[1])
  cat_label <- as.character(var[4])
  full.df[,col_nam] <- 0
  for (i in 1:nrow(full.df)){
    if(is.na(full.df[i,"pop21"])){
      next
    }
    pop_val <- as.numeric(full.df[i,"pop21"])
    if ((pop_val >= var[2]) & (pop_val < var[3])){
      full.df[i,col_nam] <- 1
      full.df[i, "pop.bin"] <- cat_label
    }
  }
}

## Time variable, 0 if 2016 and 1 if 2021
full.df <- full.df %>%
  mutate(time = ifelse(Year == 2021, 1, 0))

```

```{r}
# How many unsuitable NA values are there by population bin?


full.df[full.df$Tenure == "Total",] %>%
  group_by(pop.bin) %>%
  summarise(sum_na = sum(is.na(unsuit)))

sum(full.df$pop_1k_2.5k)
# 3267/4740 observations below 1000 have NA for count of unsuitable housing...
# whereas less than 10% of 1000 to 2500 have NAs

```

```{r}
# If I drop all obs with NA unsuit, unafford, inadq, how many are left?
df.no.nas <- full.df[!(is.na(full.df$unafford)),]
df.no.nas <- df.no.nas[!(is.na(df.no.nas$unsuit)),]
df.no.nas <- df.no.nas[!(is.na(df.no.nas$inadq)),]
df.no.nas <- df.no.nas[!(is.na(df.no.nas$cov19aid.pc)),]

print(nrow(df.no.nas))

# About 9786 out of 26913
```
```{r}
# Distribution of NA rows by pop bin
df.nas <- full.df[(is.na(full.df$unafford)),]
df.nas <- df.nas[(is.na(df.nas$unsuit)),]
df.nas <- df.nas[(is.na(df.nas$inadq)),]

df.nas %>% ggplot(aes(x=pop.bin)) + geom_bar(fill="blue") + theme_classic()
```


```{r}
##################################################
## PART B: ANALYSIS                              #
##################################################

# How do the housing indicators compare province-by-province? Use pop-based weights
# and equal weight by subdivision to analyze differences?

## Regress indicators in 2016 and 2021 separately by province 

#df.no.nas$prov <- df.no.nas$prov %>% relevel(ref="ON") # set reference category to Ontario

df.fltrd <- df.no.nas[(df.no.nas$Year == 2016) & (df.no.nas$Tenure == "Total"),]
ml.prov16 <- df.fltrd %>%
  lm(formula = unafford.pc ~ factor(prov), weights=pop16)

df.fltrd <- df.no.nas[(df.no.nas$Year == 2021) & (df.no.nas$Tenure == "Total"),]
ml.prov21 <- df.fltrd %>%
  lm(formula = unafford.pc ~ factor(prov), weights=pop21)
  
## Build dataframe: province-year, expectation, confidence interval
provs <- c("BC", "AB", "SK", "MB", "ON", "QC", "NB", "NS", "NL", "PEI")

prov.ests16 <- data.frame(prov=provs, year=2016)
predictions <- predict.lm(ml.prov16, newdata=prov.ests16, interval="confidence")
prov.ests16 <- prov.ests16 %>% cbind(predictions)

prov.ests21 <- data.frame(prov=provs, year=2021)
predictions <- predict.lm(ml.prov21, newdata=prov.ests21, interval="confidence")
prov.ests21 <- prov.ests21 %>% cbind(predictions)

prov.ests <- prov.ests16 %>% rbind(prov.ests21)
prov.ests$year <- as.character(prov.ests$year)

## Plot bars with conf intervals
unafford.by.prov <- ggplot(prov.ests, aes(x=factor(prov, provs), y=fit, fill=year)) +
  labs(title = "Prominent declines in unaffordable housing in the largest provinces",
       subtitle = "Estimates of mean unaffordable housing rate, weighted by 2016 population",
       x = "Province",
       y = "Percent",
       fill = "Year") +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(x=prov, ymin=lwr, ymax=upr), colour="black", position="dodge")

unafford.by.prov

```






```{r}
# Relative frequency of population bins by province
#df.gb <- df.no.nas[df.no.nas$Tenure == "Total", c("prov", "pop.bin")] %>% 
#  group_by(prov, pop.bin) %>% summarise(count = n())
df.gb <- df.no.nas[(df.no.nas$Tenure == "Total") & (!df.no.nas$prov %in% c("YT","NT","NU")),
                   c("prov", "pop.bin")] %>% 
  count(prov, pop.bin)
# calculate relative frequencies
df.gb$Total <- NA
for (province in provs){
  prov_total <- df.gb[df.gb$prov == province, "n"] %>% sum()
  df.gb[df.gb$prov == province, "Total"] <- prov_total
}
df.gb <- df.gb %>% mutate(rel.frq = n / Total)


# make plot
pop_order <- c("over 200,000", "50,000 to 200,000","10,000 to 50,000", 
               "2500 to 10,000", "1000 to 2500", "Below 1000")

df.gb %>% ggplot(aes(x=factor(prov, provs), y=rel.frq, fill=factor(pop.bin, pop_order))) + 
  geom_bar(stat="identity", position="fill") +
  labs(x = "Province", y = "Relative Frequency", fill = "Population")#LATER: Order by west to east, population
```

```{r}
# Relative frequency of population bins by Tenure
#df.gb <- df.no.nas[df.no.nas$Tenure == "Total", c("prov", "pop.bin")] %>% 
#  group_by(prov, pop.bin) %>% summarise(count = n())
df.gb <- df.no.nas[(df.no.nas$Tenure != "Total"),c("Tenure", "pop.bin")] %>% 
  count(Tenure, pop.bin)
# calculate relative frequencies
df.gb$Total <- NA
for (tenure_type in c("Owner", "Renter")){
  tenure_total <- df.gb[df.gb$Tenure == tenure_type, "n"] %>% sum()
  df.gb[df.gb$Tenure == tenure_type, "Total"] <- tenure_total
}
df.gb <- df.gb %>% mutate(rel.frq = n / Total)


# make plot
pop_order <- c("over 200,000", "50,000 to 200,000","10,000 to 50,000", 
               "2500 to 10,000", "1000 to 2500", "Below 1000")

df.gb %>% ggplot(aes(x=Tenure, y=rel.frq, fill=factor(pop.bin, pop_order))) + 
  geom_bar(stat="identity", position="fill") +
  labs(title = "The homeowner sample is less concentrated into larger centres compared to renters",
       subtitle = "Composition of census subdivision samples by population and tenure",
       y = "Relative Frequency", fill = "Population")
```


```{r}
## Regress indicators in 2016 and 2021 separately by Population Bin (Unfinished) 
## and graph the means w/ conf intervals


df.fltrd <- df.no.nas[(df.no.nas$Year == 2016) & (df.no.nas$Tenure == "Total"),]
ml.pop16 <- df.fltrd %>%
  lm(formula = unafford.pc ~ factor(pop.bin))

df.fltrd <- df.no.nas[(df.no.nas$Year == 2021) & (df.no.nas$Tenure == "Total"),]
ml.pop21 <- df.fltrd %>%
  lm(formula = unafford.pc ~ factor(pop.bin))
  
## Build dataframe: pop.bin-year, expectation, confidence interval
popbins <- c(unique(df.fltrd$pop.bin))

pop.ests16 <- data.frame(pop.bin=popbins, year=2016)
predictions <- predict.lm(ml.pop16, newdata=pop.ests16, interval="confidence")
pop.ests16 <- pop.ests16 %>% cbind(predictions)

pop.ests21 <- data.frame(pop.bin=popbins, year=2021)
predictions <- predict.lm(ml.pop21, newdata=pop.ests21, interval="confidence")
pop.ests21 <- pop.ests21 %>% cbind(predictions)

pop.ests <- pop.ests16 %>% rbind(pop.ests21)
pop.ests$year <- as.character(pop.ests$year)

pop_order <- c("Below 1000", "1000 to 2500","2500 to 10,000","10,000 to 50,000",
               "50,000 to 200,000", "over 200,000")

## Plot bars with conf intervals
unafford.by.pop <- ggplot(pop.ests, aes(x=factor(pop.bin, pop_order), y=fit, fill=year)) +
  labs(title = "Proportions in Unaffordable housing declining across subdivisions",
       subtitle = "Unconditional estimates of mean unaffordable housing rate",
       x = "Population Size", 
       y = "Percent", fill = "Year") +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(x=pop.bin, ymin=lwr, ymax=upr), colour="black", position="dodge")

unafford.by.pop
```

```{r}
# Repeat graph for remaining two indicators

## INADEQUATE HOUSING

df.fltrd <- df.no.nas[(df.no.nas$Year == 2016) & (df.no.nas$Tenure == "Total"),]
ml.pop16 <- df.fltrd %>%
  lm(formula = inadq.pc ~ factor(pop.bin))

df.fltrd <- df.no.nas[(df.no.nas$Year == 2021) & (df.no.nas$Tenure == "Total"),]
ml.pop21 <- df.fltrd %>%
  lm(formula = inadq.pc ~ factor(pop.bin))
  
## Build dataframe: pop.bin-year, expectation, confidence interval
popbins <- c(unique(df.fltrd$pop.bin))

pop.ests16 <- data.frame(pop.bin=popbins, year=2016)
predictions <- predict.lm(ml.pop16, newdata=pop.ests16, interval="confidence")
pop.ests16 <- pop.ests16 %>% cbind(predictions)

pop.ests21 <- data.frame(pop.bin=popbins, year=2021)
predictions <- predict.lm(ml.pop21, newdata=pop.ests21, interval="confidence")
pop.ests21 <- pop.ests21 %>% cbind(predictions)

pop.ests <- pop.ests16 %>% rbind(pop.ests21)
pop.ests$year <- as.character(pop.ests$year)

pop_order <- c("Below 1000", "1000 to 2500","2500 to 10,000","10,000 to 50,000",
               "50,000 to 200,000", "over 200,000")

## Plot bars with conf intervals
inadq.by.pop <- ggplot(pop.ests, aes(x=factor(pop.bin, pop_order), y=fit, fill=year)) +
  labs(title = "Canada's smallest communities face higher proportions of Inadequate housing",
       subtitle = "Unconditional estimates of mean inadequate housing rate",
       x = "Population Size", 
       y = "Percent", fill = "Year") +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(x=pop.bin, ymin=lwr, ymax=upr), colour="black", position="dodge")

inadq.by.pop


```

```{r}
## UNSUITABLE HOUSING

df.fltrd <- df.no.nas[(df.no.nas$Year == 2016) & (df.no.nas$Tenure == "Total"),]
ml.pop16 <- df.fltrd %>%
  lm(formula = unsuit.pc ~ factor(pop.bin))

df.fltrd <- df.no.nas[(df.no.nas$Year == 2021) & (df.no.nas$Tenure == "Total"),]
ml.pop21 <- df.fltrd %>%
  lm(formula = unsuit.pc ~ factor(pop.bin))
  
## Build dataframe: pop.bin-year, expectation, confidence interval
popbins <- c(unique(df.fltrd$pop.bin))

pop.ests16 <- data.frame(pop.bin=popbins, year=2016)
predictions <- predict.lm(ml.pop16, newdata=pop.ests16, interval="confidence")
pop.ests16 <- pop.ests16 %>% cbind(predictions)

pop.ests21 <- data.frame(pop.bin=popbins, year=2021)
predictions <- predict.lm(ml.pop21, newdata=pop.ests21, interval="confidence")
pop.ests21 <- pop.ests21 %>% cbind(predictions)

pop.ests <- pop.ests16 %>% rbind(pop.ests21)
pop.ests$year <- as.character(pop.ests$year)

pop_order <- c("Below 1000", "1000 to 2500","2500 to 10,000","10,000 to 50,000",
               "50,000 to 200,000", "over 200,000")

## Plot bars with conf intervals
unsuit.by.pop <- ggplot(pop.ests, aes(x=factor(pop.bin, pop_order), y=fit, fill=year)) +
  labs(title = "Unsuitable housing is concentrated in Canada's largest and smallest centres",
       subtitle = "Unconditional estimates of mean unsuitable housing rate",
       x = "Population Size", 
       y = "Percent", fill = "Year") +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(x=pop.bin, ymin=lwr, ymax=upr), colour="black", position="dodge")

unsuit.by.pop
```


```{r}
# Regression analysis using OLS model - housing indicators ~ pop size, covar's
# Do separate regressions for owner sample, renter sample, whole sample
```

```{r}
# Regress restricting to 2016 and 2021 samples, drop where unafford == NA.
# Use for reporting unweighted means of each community group, over time 

model.tot2021 <- df.no.nas[(df.no.nas$Tenure == "Total") & (df.no.nas$Year == 2021),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k)

print("FIRST REGRESSION")
#summary(model.tot2021)

model.tot2016 <- df.no.nas[(df.no.nas$Tenure == "Total") & (df.no.nas$Year == 2016),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k)

print("SECOND REGRESSION")
#summary(model.tot2016)
```

```{r}
### MAIN Regression - How have housing indicators changed over time for each group ###

## 1. UNAFFORDABLE HOUSING 
### w/o size/year interactions
model.tot1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time)

# summary(model.tot1)
```


```{r}
### with interactions
model.tot2 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k)

# summary(model.tot2)
```
Unconditional on covariates, change over the censuses of housing unaffordability  
not statistically different from the change in Canada's largest cities. 

```{r}
### with covariates (non-family, age)
model.tot3 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp)

# summary(model.tot3)
```
Income, population density and education controls eliminate mean differences between
the population groups. Implies unaffordability not due to differences in population size per se,
but rather associated with income and education differences. I tried removing population density
and mean differences returns to significance. Conditional on these controls, little to no differences
in housing affordability for settlements > 10K people.

```{r}
### with family, age covariates
model.tot4 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus)

# summary(model.tot4)
```
Ages have negative association with housing affordability, controlling for the other factors. 
But having children has a positive association...

```{r}
### Fixed Effects with Indigenous community indicator
model.tot5 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

# summary(model.tot5)
```
Provincial fixed effects eliminate significance of estimates for all population
groupings except for 1K-2.5K group.

```{r}
### One last check: restricted to 2021 sample, with % pop change as regressor
df.2021 <- df.no.nas[(df.no.nas$Year == 2021),]

model.pop.chg <- df.2021 %>% 
  lm(formula = unafford.pc ~ pop_chg + pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

# summary(model.pop.chg)
```



```{r}
### TABLE 1: Change over time of indicators, unaffordable

### NOTE: model names shorten to m1, m2, etc. due to bug in stargazer not 
### liking model names too long. 

#### Total, no controls
m1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k)

#### Total, w/ controls
m2 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))


#### Total, w/ base controls and adl COVID-19 controls
m3 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

#### Owner, no controls
m4 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k)

#### Owner, w/ controls
m5 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

#### Owner, w/ base controls and adl COVID-19 controls
m6 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

#### Renter, no controls
m7 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k)

#### Renter, w/ controls
m8 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

#### Renter, w/ base controls and adl COVID-19 controls
m9 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_50k_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_50k_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)


stargazer(m1, m2, m3, m4, m5, m6, 
          m7, m8, m9,
          align=TRUE, type="text",
          title = "Regression Estimates, Unaffordability",
          keep=c("Constant","pop_bel_1k","pop_1k_2.5k","pop_2.5k_10k","pop_10k_50k","pop_50k_200k",
                 "pop_bel_1k:time","pop_1k_2.5k:time","pop_2.5k_10k:time","pop_10k_50k:time",
                 "pop_50k_200k:time", "time"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          column.labels = c("Total Sample", "Homeowners", "Renters"),
          column.separate = c(3,3,3),
          notes = "Reference category: Population > 200,000",
          add.lines = list(c("COVID-19 Controls", "No", "No", "Yes", "No", "No", "Yes", "No", "No", "Yes"),
                           c("Base Controls", "No", "Yes", "Yes", "No", "Yes", "Yes", "No", "Yes", "Yes")))

```

```{r}
### TABLE 1a: Swapping to 50-200k as omitted category
#### Total, no controls
m1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se1 <- vcovHC(m1, type="HC2") %>% diag() %>% sqrt()

#### Total, w/ controls
m2 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se2 <- vcovHC(m2, type="HC2") %>% diag() %>% sqrt()


#### Total, w/ base controls and adl COVID-19 controls
m3 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se3 <- vcovHC(m3, type="HC2") %>% diag() %>% sqrt()

#### Owner, no controls
m4 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se4 <- vcovHC(m4, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ controls
m5 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se5 <- vcovHC(m5, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ base controls and adl COVID-19 controls
m6 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se6 <- vcovHC(m6, type="HC2") %>% diag() %>% sqrt()

#### Renter, no controls
m7 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se7 <- vcovHC(m7, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ controls
m8 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se8 <- vcovHC(m8, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ base controls and adl COVID-19 controls
m9 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se9 <- vcovHC(m9, type="HC2") %>% diag() %>% sqrt()

models <- list(m1,m2,m3,m4,m5,m6,m7,m8,m9)

robust.se <- list(r.se1, r.se2, r.se3, r.se4, r.se5, r.se6, r.se7, r.se8, r.se9)


stargazer(models,
          se = robust.se,
          align=TRUE, type="text",
          title = "Regression Estimates, Unaffordability",
          keep=c("Constant","pop_bel_1k","pop_1k_2.5k","pop_2.5k_10k","pop_10k_50k","pop_abv_200k",
                 "pop_bel_1k:time","pop_1k_2.5k:time","pop_2.5k_10k:time","pop_10k_50k:time",
                 "pop_abv_200k:time", "time"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          column.labels = c("Total Sample", "Homeowners", "Renters"),
          column.separate = c(3,3,3),
          notes = "Reference category: Population between 50K & 200K",
          add.lines = list(c("COVID-19 Controls", "No", "No", "Yes", "No", "No", "Yes", "No", "No", "Yes"),
                           c("Base Controls", "No", "Yes", "Yes", "No", "Yes", "Yes", "No", "Yes", "Yes")))
```


```{r}
### TABLE 2: Change over time of indicators, unsuitable
#### Total, no controls
m1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se1 <- vcovHC(m1, type="HC2") %>% diag() %>% sqrt()

#### Total, w/ controls
m2 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se2 <- vcovHC(m2, type="HC2") %>% diag() %>% sqrt()


#### Total, w/ base controls and adl COVID-19 controls
m3 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se3 <- vcovHC(m3, type="HC2") %>% diag() %>% sqrt()

#### Owner, no controls
m4 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se4 <- vcovHC(m4, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ controls
m5 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se5 <- vcovHC(m5, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ base controls and adl COVID-19 controls
m6 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se6 <- vcovHC(m6, type="HC2") %>% diag() %>% sqrt()

#### Renter, no controls
m7 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se7 <- vcovHC(m7, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ controls
m8 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se8 <- vcovHC(m8, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ base controls and adl COVID-19 controls
m9 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se9 <- vcovHC(m9, type="HC2") %>% diag() %>% sqrt()

models <- list(m1,m2,m3,m4,m5,m6,m7,m8,m9)

robust.se <- list(r.se1, r.se2, r.se3, r.se4, r.se5, r.se6, r.se7, r.se8, r.se9)




stargazer(m1, m2, m3, m4, m5, m6, 
          m7, m8, m9,
          se = robust.se,
          align=TRUE, type="text",
          title = "Regression Estimates, Unsuitable Housing",
          keep=c("Constant","pop_bel_1k","pop_1k_2.5k","pop_2.5k_10k","pop_10k_50k","pop_abv_200k",
                 "pop_bel_1k:time","pop_1k_2.5k:time","pop_2.5k_10k:time","pop_10k_50k:time",
                 "pop_abv_200k:time", "time"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          column.labels = c("Total Sample", "Homeowners", "Renters"),
          column.separate = c(3,3,3),
          notes = "Reference category: Population between 50K and 200K",
          add.lines = list(c("COVID-19 Controls", "No", "No", "Yes", "No", "No", "Yes", "No", "No", "Yes"),
                           c("Base Controls", "No", "Yes", "Yes", "No", "Yes", "Yes", "No", "Yes", "Yes")))

```

```{r}
### TABLE 3: Change over time of indicators, inadequate
#### Total, no controls
m1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se1 <- vcovHC(m1, type="HC2") %>% diag() %>% sqrt()

#### Total, w/ controls
m2 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se2 <- vcovHC(m2, type="HC2") %>% diag() %>% sqrt()


#### Total, w/ base controls and adl COVID-19 controls
m3 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se3 <- vcovHC(m3, type="HC2") %>% diag() %>% sqrt()

#### Owner, no controls
m4 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se4 <- vcovHC(m4, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ controls
m5 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se5 <- vcovHC(m5, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ base controls and adl COVID-19 controls
m6 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se6 <- vcovHC(m6, type="HC2") %>% diag() %>% sqrt()

#### Renter, no controls
m7 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k)

r.se7 <- vcovHC(m7, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ controls
m8 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se8 <- vcovHC(m8, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ base controls and adl COVID-19 controls
m9 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se9 <- vcovHC(m9, type="HC2") %>% diag() %>% sqrt()

models <- list(m1,m2,m3,m4,m5,m6,m7,m8,m9)

robust.se <- list(r.se1, r.se2, r.se3, r.se4, r.se5, r.se6, r.se7, r.se8, r.se9)


stargazer(m1, m2, m3, m4, m5, m6, 
          m7, m8, m9,
          se = robust.se,
          align=TRUE, type="text",
          title = "Regression Estimates, Inadequate Housing",
          keep=c("Constant","pop_bel_1k","pop_1k_2.5k","pop_2.5k_10k","pop_10k_50k","pop_abv_200k",
                 "pop_bel_1k:time","pop_1k_2.5k:time","pop_2.5k_10k:time","pop_10k_50k:time",
                 "pop_abv_200k", "time"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          column.labels = c("Total Sample", "Homeowners", "Renters"),
          column.separate = c(3,3,3),
          notes = "Reference category: Population between 50K and 200K",
          add.lines = list(c("Weights", "No", "No", "Yes", "No", "No", "Yes", "No", "No", "Yes"),
                           c("Controls", "No", "Yes", "Yes", "No", "Yes", "Yes", "No", "Yes", "Yes")))

```

```{r}
# Presentation table: regression results for full control set, split by tenure, for all vars

## UNAFFORDABLE HOUSING
#### Total, w/ base controls and adl COVID-19 controls
m1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se1 <- vcovHC(m1, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ base controls and adl COVID-19 controls
m2 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se2 <- vcovHC(m2, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ base controls and adl COVID-19 controls
m3 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se3 <- vcovHC(m3, type="HC2") %>% diag() %>% sqrt()

## INADEQUATE HOUSING
#### Total, w/ base controls and adl COVID-19 controls
m4 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se4 <- vcovHC(m4, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ base controls and adl COVID-19 controls
m5 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se5 <- vcovHC(m5, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ base controls and adl COVID-19 controls
m6 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = inadq.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se6 <- vcovHC(m6, type="HC2") %>% diag() %>% sqrt()


## UNSUITABLE HOUSING
#### Total, w/ base controls and adl COVID-19 controls
m7 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se7 <- vcovHC(m7, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ base controls and adl COVID-19 controls
m8 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se8 <- vcovHC(m8, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ base controls and adl COVID-19 controls
m9 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unsuit.pc ~ pop_bel_1k + pop_1k_2.5k + pop_2.5k_10k + pop_10k_50k + pop_abv_200k + time +
       time*pop_bel_1k + time*pop_1k_2.5k + time*pop_2.5k_10k + time*pop_10k_50k + time*pop_abv_200k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se9 <- vcovHC(m9, type="HC2") %>% diag() %>% sqrt()

# BUILD TABLE
robust.se <- list(r.se1, r.se2, r.se3, r.se4, r.se5, r.se6, r.se7, r.se8, r.se9)


stargazer(m1, m2, m3, m4, m5, m6, 
          m7, m8, m9,
          se = robust.se,
          align=TRUE, type="text",
          title = "Regression Estimates By Tenure",
          keep=c("pop_bel_1k:time","pop_1k_2.5k:time","pop_2.5k_10k:time","pop_10k_50k:time",
                 "pop_abv_200k:time", "time"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          #covariate.labels = c("Time", "Below 1000 * Time", "1000 to 2500 * Time", "2500 to 10,000 * Time",
          #                     "10,000 to 50,000 * Time", "Above 200,000 * Time"),
          column.labels = c("Total", "Owners", "Renters","Total", "Owners", "Renters",
                            "Total", "Owners", "Renters"),
          dep.var.labels = c("Unaffordable Housing", "Inadequate Housing", "Unsuitable Housing"),
          column.separate = c(1,1,1,1,1,1,1,1,1),
          notes = "Reference category: Population between 50K and 200K",
          add.lines = list(c("COVID-19 Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Base Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))

```

```{r}
# Build table above including population coefficients (for appendix)

stargazer(m1, m2, m3, m4, m5, m6, 
          m7, m8, m9,
          se = robust.se,
          align=TRUE, type="text",
          title = "Regression Estimates By Tenure",
          keep=c("pop_bel_1k:time","pop_1k_2.5k:time","pop_2.5k_10k:time","pop_10k_50k:time",
                 "pop_abv_200k:time", "time", "pop_bel_1k", "pop_1k_2.5k", "pop_2.5k_10k", 
                 "pop_10k_50k", "pop_abv_200k"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          covariate.labels = c("Below 1000", "1000 to 2500", "2500 to 10,000", "10,000 to 50,000", 
                               "Above 200,000", "Time", "Below 1000 * Time", "1000 to 2500 * Time", 
                               "2500 to 10,000 * Time", "10,000 to 50,000 * Time", 
                               "Above 200,000 * Time"),
          column.labels = c("Total", "Owners", "Renters","Total", "Owners", "Renters",
                            "Total", "Owners", "Renters"),
          dep.var.labels = c("Unaffordable Housing", "Inadequate Housing", "Unsuitable Housing"),
          column.separate = c(1,1,1,1,1,1,1,1,1),
          notes = "Reference category: Population between 50K and 200K",
          add.lines = list(c("COVID-19 Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Base Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))
```



```{r}
# Are results robust to binning? Trying under 65K/over 65K bins like in F&K 2013

### order: list(var_name, lower_bound, upper_bound)
city_params <- list(
  list("pop_bel_65k", 0, 65000, "Below 65000"),
  list("pop_abv_65k", 65000, max(df.no.nas$pop21, na.rm=TRUE) + 1, "over 65000") # max value plus 1, see comment below 
  ### because will use < for second value. see code below.
)

for (var in city_params){
  col_nam <- as.character(var[1])
  cat_label <- as.character(var[4])
  df.no.nas[,col_nam] <- 0
  for (i in 1:nrow(df.no.nas)){
    if(is.na(df.no.nas[i,"pop21"])){
      next
    }
    pop_val <- as.numeric(df.no.nas[i,"pop21"])
    if ((pop_val >= var[2]) & (pop_val < var[3])){
      df.no.nas[i,col_nam] <- 1
    }
  }
}

## Build Regression Table

#### Total, no controls
m1 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k)

r.se1 <- vcovHC(m1, type="HC2") %>% diag() %>% sqrt()

#### Total, w/ controls
m2 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se2 <- vcovHC(m2, type="HC2") %>% diag() %>% sqrt()

#### Total, w/ Base controls & COVID controls
m3 <- df.no.nas[(df.no.nas$Tenure == "Total"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se3 <- vcovHC(m3, type="HC2") %>% diag() %>% sqrt()

#### Owner, no controls
m4 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k)

r.se4 <- vcovHC(m4, type="HC2") %>% diag() %>% sqrt()

#### Owner, w/ controls
m5 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se5 <- vcovHC(m5, type="HC2") %>% diag() %>% sqrt()

#### Owners, base & COVID controls
m6 <- df.no.nas[(df.no.nas$Tenure == "Owner"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se6 <- vcovHC(m6, type="HC2") %>% diag() %>% sqrt()

#### Renter, no controls
m7 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k)

r.se7 <- vcovHC(m7, type="HC2") %>% diag() %>% sqrt()

#### Renter, w/ controls
m8 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov))

r.se8 <- vcovHC(m8, type="HC2") %>% diag() %>% sqrt()

#### Renters, base & COVID controls
m9 <- df.no.nas[(df.no.nas$Tenure == "Renter"),] %>% 
  lm(formula = unafford.pc ~ pop_bel_65k + time + time*pop_bel_65k +
       med_at_inc + bel_lico + non_cdn + he_highschool + he_postsec + unemp + married +
       marr_w_child + age_15to24 + age_25to34 + age_35to44 + age_45to54 + age_55to64 +
       age_65to74 + age_75to84 + age_85_plus + factor(prov) + av_cov19aid + cov19aid.pc)

r.se9 <- vcovHC(m9, type="HC2") %>% diag() %>% sqrt()

robust.se <- list(r.se1, r.se2, r.se3, r.se4, r.se5, r.se6, r.se7, r.se8, r.se9)

stargazer(m1, m2, m3, m4, m5, m6, m7, m8, m9,
          se = robust.se,
          align=TRUE, type="text",
          title = "Regression Estimates, Unaffordability",
          keep=c("Constant", "pop_bel_65k",
                 "pop_bel_65k:time", "time"),
          omit.stat = c("f","adj.rsq", "ser"),
          column.sep.width = "1pt", 
          font.size="scriptsize",
          float.env="sidewaystable",
          column.labels = c("Total Sample", "Homeowners", "Renters"),
          column.separate = c(3,3,3),
          notes = "Reference category: Population > 65,000",
          add.lines = list(c("COVID-19 Controls", "No", "No", "Yes", "No", "No", "Yes", "No", "No", "Yes"),
                           c("Controls", "No", "Yes", "Yes", "No", "Yes", "Yes", "No", "Yes", "Yes")))


```



```{r}
# get summary statistics: group by year-tenure type

vars.of.int <- c("tot.hh", "inadq.pc", "unsuit.pc", "unafford.pc")

stats <- c("mean(x)", "sd(x)", "min(x)", "median(x)", "max(x)", "notNA(x)")
stats.label <- c("Mean", "Std. Dev.", "Min", "Median", "Max", "Obs.")

sumtable(df.no.nas[df.no.nas$Tenure == "Total",], vars=vars.of.int, summ=stats, summ.names=stats.label, group="Tenure", out="latexpage") 
# NOTE: This only looks at total part of sample because I changed it for
# presentation.
```

```{r}
# Distributions of the rates of the housing indicators

f_path = "C:/Users/marti/Documents/GitHub/ECO475-Paper/Output" # for storing output

## Unaffordable housing
hist.d <- df.no.nas[(df.no.nas$Tenure == "Total"),]
hist.d %>% ggplot(aes(x=unafford.pc)) +
  geom_histogram(position="identity", fill="orange", binwidth = 3) +
  ggtitle("Unaffordable Housing Distribution, Total Sample") + xlab("Unaffordable Housing (%)")

hist.d <- df.no.nas[(df.no.nas$Tenure == "Owner") | (df.no.nas$Tenure == "Renter"),]
graph1 <- hist.d %>% ggplot(aes(x=unafford.pc, fill=Tenure)) + geom_histogram(alpha=0.6, position="identity", binwidth = 3) + ggtitle("Unaffordable Housing Distribution, Owner & Renter") + xlab("Unaffordable Housing (%)")

## Unsuitable housing
hist.d <- df.no.nas[(df.no.nas$Tenure == "Total"),]
hist.d %>% ggplot(aes(x=unsuit.pc)) +
  geom_histogram(position="identity", fill="orange", binwidth = 3) +
  ggtitle("Unsuitable Housing Distribution, Total Sample") + xlab("Unsuitable Housing (%)")

hist.d <- df.no.nas[(df.no.nas$Tenure == "Owner") | (df.no.nas$Tenure == "Renter"),]
graph2 <- hist.d %>% ggplot(aes(x=unsuit.pc, fill=Tenure)) + geom_histogram(alpha=0.6, position="identity", binwidth = 3) + ggtitle("Unsuitable Housing Distribution, Owner & Renter") + xlab("Unsuitable Housing (%)")



## Inadequate housing
hist.d <- df.no.nas[(df.no.nas$Tenure == "Total"),]
hist.d %>% ggplot(aes(x=inadq.pc)) +
  geom_histogram(position="identity", fill="orange", binwidth = 3) +
  ggtitle("Inadequate Housing Distribution, Total Sample") + xlab("Inadequate Housing (%)")

hist.d <- df.no.nas[(df.no.nas$Tenure == "Owner") | (df.no.nas$Tenure == "Renter"),]
graph3 <- hist.d %>% ggplot(aes(x=inadq.pc, fill=Tenure)) + geom_histogram(alpha=0.6, position="identity", binwidth = 3) + ggtitle("Inadequate Housing Distribution, Owner & Renter") + xlab("Inadequate Housing (%)")


ggarrange(graph1, graph2, graph3, nrow = 2, ncol = 2)
ggsave(filename = "dists.png", width = 40, height = 20, units = "cm", path = f_path)

```

```{r}
# Combine unaffordable housing graphs by population and province
ggarrange(unafford.by.pop, unafford.by.prov, nrow = 1, ncol = 2)
ggsave(filename = "unafford_ests.png", width = 40, height = 15, units = "cm", path = f_path)

```


```{r}
# Summary Statistics for dependent variables

## Total Sample
df_subset <- df.no.nas

stargazer(df_subset, type = "text")

```


```{r}
# Summary Statistics for controls; segmented by Tenure
vars.of.int <- c("married", "marr_w_child", "cov19aid.pc",
                 "av_cov19aid", "med_at_inc","bel_lico","age_15to24","age_25to34","age_35to44",
                 "age_45to54", "age_55to64", "age_65to74", "age_75to84", "age_85_plus", "non_cdn",
                 "he_highschool", "he_postsec", "unemp")

stats <- c("mean(x)", "sd(x)", "min(x)", "median(x)", "max(x)", "notNA(x)")
stats.label <- c("Mean", "Std. Dev.", "Min", "Median", "Max", "Obs.")

sumtable(df.no.nas, vars=vars.of.int, summ=stats, summ.names=stats.label, group="Tenure", out="browser")
```


```{r}
### HELPER FUNCTIONS ###
#function encode_dummy(data, new_var, logical) # use logical to code dummy variable new_var = 1


```


```{}
# SCRAP CODE

housing.w <- apply_labels(housing.w,
  tot.hh = "Total Households",
  inadq.pc = "Inadequate Housing (%)",
  inadq = "Inadequate Housing (Count)",
  unsuit.pc = "Unsuitable Housing (%)",
  unsuit = "Unsuitable Housing (Count)",
  unafford.pc = "Unaffordable Housing (%)",
  unafford = "Unaffordable Housing (Count)",
  core.nd.pc = "In Core Housing Need (%)",
  core.nd = "In Core Housing Need (Count)"
)
```

